Estimating Gaze Duration Error Distributions from Eye Tracking Data

### 2022-06-29 paper/paper.tex
Changing density of experiments

As shown in Figure \ref{fig:fixation_vs_duration} we see

We show all experimental results in Figure \ref{fig:plots}. The top series corresponds
to experiments where the AOI is the top third of the viewport, the middle and bottom 
series correspond to their respective thirds of the viewport. In each plot we show
data for a specific session length ranging from 10 to 30 seconds, where the x axis
depicts the measured gaze duration and the y-axis shows the confidence range for the
true gaze duration.

@@

>>>>

As shown in Figure \ref{fig:fixation_vs_duration} we see that the error in gaze duration
grows with error in fixation points, as would be expected. However, when we use the exponential
weighting to calculate the expected error in duration, the gaze duration error grows much slower
than in the uniform case. This suggests that the observed tendency toward smaller measurements
in area of interest studies means lower expected error.

In our final experiment we look at the effect of both the size of the measured 
gaze duration and the mean error of fixation on the expected error in gaze duration.

@@

We have demonstrated that the statistial information contained in eye tracking validation
data can be utilised for estimating errors in gaze duration estimation. The process involves
simulating the distribution of measurements for a given true durastion, and then inverting
it into a distribution over true duration for a given measurement.

We have released this approach as the open source application gazerr, and used it to explore
the relationship between fixation error and duration error. Our results show that the nature
of the error in gaze duration depends on the size of the measurement. Smaller measurements
tend toward over prediction, and larger measurements towards under prediction. We plotted
the relationship between expected error and saw that observed tendency toward smaller duration
measurements (estimated with an psuedo-exponential distribution) delivers a slower growing
expected duraiton error with the mean error in fixation points.

Finally, our simualtions revealed that for large error in fixation points certain measurements
become some unlikely that our monte carlo simualtions placed none of the probability density
in those regions. This strongly suggests that an additional downside to large fixation point error
is a reduced range of measurement for area of interest studies.
